---
title: "Fraud Analysis using K-Means Algorithm"
author: "Yaumil Sitta"
date: "`r format(Sys.Date(), '%B %e, %Y')`"
output: 
  html_document:
    df_print: paged
    toc: true
    toc_depth: 2
    toc_float: true
    theme: united
    highlight: espresso
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)
```

# Unsupervised Learning

Imagine you have a dataset and have no variable that you will predict. In case you have a datasets with no target variable, the learning of a machine has to be unsupervised. Hence the learning will be done based on several measure of similarity or distance between each observation in the dataset. The most commonly used technique in supervised learning is clustering.

<center>

![Source: [Research Gate](https://www.researchgate.net/figure/Supervised-learning-and-unsupervised-learning-Supervised-learning-uses-annotation_fig1_329533120)](assets/Supervised vs Unsup.png)


</center>

# Clustering Analysis

[Cluster analysis](https://en.wikipedia.org/wiki/Cluster_analysis) or clustering is the task of grouping a set of objects in such a way that objects in the same group (called a cluster) are more similar (in some sense) to each other than to those in other groups (clusters). In this article, we will discuss about one of the common clustering algorithms, that is kmeans.

# Kmeans Clustering Analysis

K-means is a centroid-based clustering algorithm that follows a simple procedure of classifying a given dataset into a pre-determined number of clusters, denoted as “k”. We will discuss about one use case that can be done using kmeans algorithm.

The use case that will be discuss here is fraud analysis in mobile financial industry.

```{r}
library(tidyverse)
library(factoextra)
```

```{r}
paysim <- read_csv("paysim1.csv")
```

PaySim simulates mobile money transactions based on a sample of real transactions extracted from one month of financial logs from a mobile money service implemented in an African country. The original logs were provided by a multinational company, who is the provider of the mobile financial service which is currently running in more than 14 countries all around the world. The dataset is downloaded from [kaggle](https://www.kaggle.com/ntnu-testimon/paysim1).

```{r}
fr <- paysim %>% 
  filter(Fraud == "Yes" & amount == 0)
summary(fr)
summary(paysim)
```


```{r echo = F}
paysim <- paysim %>% 
  mutate(type = as.factor(type),
         Fraud = as.factor(Fraud), 
         FlaggedFraud = as.factor(FlaggedFraud)) %>% 
  filter(type == "TRANSFER" | type == "CASH_OUT") %>% 
  filter(newbalanceOrig == 0 & oldbalanceOrg != 0 & amount != 0) %>% 
 select(-step)
```

```{r}
table(paysim$Fraud == "Yes")
```


```{r}
head(paysim)
```

Variables Description:   

- `step` = maps a unit of time in the real world. In this case 1 step is 1 hour of time. Total steps 744 (30 days simulation).    
- `type` = CASH-IN, CASH-OUT, DEBIT, PAYMENT and TRANSFER.   
- `amount` = amount of the transaction in local currency.    
- `nameOrig` = customer who started the transaction    
- `oldbalanceOrg` = initial balance before the transaction    
- `newbalanceOrig` = new balance after the transaction    
- `nameDest` = customer who is the recipient of the transaction    
- `oldbalanceDest` = initial balance recipient before the transaction. Note that there is not information for customers that start with M (Merchants).   
- `newbalanceDest` = new balance recipient after the transaction. Note that there is not information for customers that start with M (Merchants).    
- `Fraud` = This is the transactions made by the fraudulent agents inside the simulation. In this specific dataset the fraudulent behavior of the agents aims to profit by taking control or customers accounts and try to empty the funds by transferring to another account and then cashing out of the system.    
- `FlaggedFraud` = The business model aims to control massive transfers from one account to another and flags illegal attempts. An illegal attempt in this dataset is an attempt to transfer more than 200.000 in a single transaction.    


```{r}
paysim_num <- paysim %>% 
  select_if(is.numeric) %>% 
  scale()

paysim_num <- as.data.frame(paysim_num) %>% 
  select(-c(newbalanceOrig, oldbalanceDest))
```


```{r}
wss <- function(data, maxCluster = 9) {
    # Initialize within sum of squares
    SSw <- (nrow(data) - 1) * sum(apply(data, 2, var))
    SSw <- vector()
    for (i in 2:maxCluster) {
        SSw[i] <- sum(kmeans(data, centers = i)$withinss)
    }
    plot(1:maxCluster, SSw, type = "o", xlab = "Number of Clusters", ylab = "Within groups sum of squares", pch=19)
}
```

```{r}
options(scipen = 999)
wss(paysim_num)
```

The elbow curve suggests that with four clusters, we were able to explain most
of the variance in data. Beyond five clusters adding more clusters is not helping with
explaining the groups (WCSS is saturating after four).

```{r}
RNGkind(sample.kind = "Rounding")
set.seed(100)
pay_km <- kmeans(paysim_num, centers = 6)
```

```{r}
paysim$cluster <- pay_km$cluster
```


```{r}
paysim_num
```

```{r}
paysim %>% 
  select(-c(type,nameOrig, nameDest, Fraud, FlaggedFraud)) %>% 
  group_by(cluster) %>% 
  summarise_all("mean")
```

```{r}
paysim %>% 
  select(-c(type,nameOrig, nameDest, FlaggedFraud)) %>% 
  group_by(Fraud) %>% 
  summarise_all("mean")
```

```{r}
table(paysim$Fraud, paysim$cluster)
```


```{r}
fviz_cluster(pay_km, paysim_num)
```



```{r}
paysim %>% 
  filter(newbalanceOrig == 0)
```


# Another cases of unsupervised learning
1. [Clustering AirBnB Review](https://arxiv.org/pdf/1705.03134.pdf)
2. [Why Tourists Choose Airbnb: A Motivation-Based Segmentation Study](https://www.researchgate.net/publication/316533754_Why_Tourists_Choose_Airbnb_A_Motivation-Based_Segmentation_Study)
3. [Clustering the weapon in PUBG game ](https://algorit.ma/blog/data-science-analysis-pubg/?utm_source=Instagram&utm_medium=Social&utm_campaign=Blog)
4. [A Taxi Driving Fraud Detection System](https://ieeexplore.ieee.org/abstract/document/6137222?utm_source=datafloq&utm_medium=ref&utm_campaign=datafloq)